TENDOR-BASED DICTIONARY LEARNING FOR FRAUD DETECTION FROM UNBALANCED DATA

### 2017-10-15 docs/papers/2018ICASSP/2018icassp.tex
baseline for icassp 2018 paper

\documentclass[conference]{IEEEtran}

\ifCLASSINFOpdf
\else
\fi

\hyphenation{op-tical net-works semi-conduc-tor}

%% packages
% graph
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{rotating}
\usepackage{tabularx}
% math
\usepackage{amsfonts}
\usepackage{mathtools}
% algorithm
\usepackage{algorithm,algorithmic}% http://ctan.org/pkg/algorithms

\begin{document}

\title{A Distributed and Tensor-based Approach for Multidimensional Dictionary Learning}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Thiago P de B Vieira}
\IEEEauthorblockA{
	Department of Electrical Engineering\\
	University of Brasilia\\
	Bras\'ilia-DF, Brazil\\
	Emai	l: tpbvieira@gmail.com
}

\and

\IEEEauthorblockN{Andr\'e L. F. de Almeida}
\IEEEauthorblockA{
	Department of Teleinformatics Engineering\\
	Federal University of Cear\'a\\
	Fortaleza, Brazil\\
	Emai	l: andre.almeida@ieee.org
}

\and

\IEEEauthorblockN{Florian Roemer\\ and Jo\~ao Paulo C. L. da Costa}
\IEEEauthorblockA{
	Institute for Information Technology\\
	Ilmenau University of Technology\\
	Ilmenau, Germany
}

}

\maketitle

\begin{abstract}
The abstract goes here.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}

Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, classification, data decomposition, feature extraction and image processing \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

@@

\section*{Acknowledgment}
{\small This research was supported by ...}

\bibliographystyle{IEEEtran}
\bibliography{references}

>>>>

% Template for ICASSP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}

%% packages
\usepackage{spconf}
% graph
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{rotating}
\usepackage{tabularx}
% math
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
% algorithm
\usepackage{algorithm,algorithmic}% http://ctan.org/pkg/algorithms

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{TENDOR-BASED DICTIONARY LEARNING FOR FRAUD DETECTION FROM UNBALANCED DATA}
%
% Single address.
% ---------------
\name{Thiago P. de B. Vieira and Jo\~ao Paulo C. L. da Costa}
\address{University of Bras\'ilia}

%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle

\begin{abstract}
The abstract goes here...
\end{abstract}

\begin{keywords}
Tensor-Based Dictionary Learning, Fraud Detection, Classification, Unbalanced Data
\end{keywords}

\section{Introduction}
\label{sec:introduction}
Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

@@

% References should be produced using the bibtex program from suitable BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\vfill\pagebreak
\bibliographystyle{IEEEbib}
\bibliography{references}
